Autocorrelation in Sparse Distributed Memory

### 2018-08-22 Chapters/sdm-autocorrelation.tex
wtf no graphics?
some fucking graphics finally appear

% !TEX root = ../partial-sdm.tex

@@

\includegraphics[width=\textwidth]{images02/autocorrelation/autocorrelation_n=1000_closeview=False.eps}

@@

\begin{figure}[!htb]
  \centering
  \includegraphics[width=0.75\textwidth]{./images02/sdm-10000bits-10000w-table-7-2.png}

@@

\begin{figure}[h!]
  \centering
  \includegraphics[width=0.75\textwidth]{./images02/autocorrelation/same-bit-histogram.png}

@@

\begin{figure}[h!]
  \centering
  \subfloat[$\text{addr}_i=1$]{\includegraphics[width=0.5\textwidth]{./images02/autocorrelation/x_at_x_addr1.png}}
  \subfloat[$\text{addr}_i=0$]{\includegraphics[width=0.5\textwidth]{./images02/autocorrelation/x_at_x_addr0.png}}

@@

\begin{figure}[h!]
  \centering
  \subfloat[``random at x'']{\includegraphics[width=0.5\textwidth]{./images02/autocorrelation/random_at_x_counters.png}}
  \subfloat[``x at x'']{\includegraphics[width=0.5\textwidth]{./images02/autocorrelation/x_at_x_counters.png}}

@@

\begin{figure}[h!]
  \centering
  \subfloat[Equation \ref{eqn:sdm-eta1-addr1}  ($\text{addr}_k=1)$]{\includegraphics[width=0.5\textwidth]{./images02/autocorrelation/read-counters-eta1_addr1.png}}
  \subfloat[Equation \ref{eqn:sdm-eta1-addr0} ($\text{addr}_k=0$)]{\includegraphics[width=0.5\textwidth]{./images02/autocorrelation/read-counters-eta1_addr0.png}}

@@

\begin{figure}[h!]
  \centering
  \subfloat[Equation \ref{eqn:sdm-eta1}  ($\eta_k=1)$]{\includegraphics[width=0.5\textwidth]{./images02/autocorrelation/read-counters-eta1.png}}
  \subfloat[Equation \ref{eqn:sdm-eta0} ($\eta_k=0$)]{\includegraphics[width=0.5\textwidth]{./images02/autocorrelation/read-counters-eta0.png}}

@@

\begin{figure}[!htb]
  \centering
  \includegraphics[width=0.6\textwidth]{./images02/autocorrelation/read-random-bs.png}

@@

\begin{figure}[!htb]
  \centering
  \includegraphics[width=0.6\textwidth]{./images02/autocorrelation/single-read-dist.png}

>>>>

% !TEX root = ../paperIEEE.tex

@@

\includegraphics[width=0.5\textwidth]{./images02/autocorrelation/autocorrelation_n=1000_closeview=False.eps}

@@

\begin{figure}[!htb]
  \centering
  \includegraphics[width=0.5\textwidth]{./images02/sdm-10000bits-10000w-table-7-2.png}

@@

\begin{figure}[h!]
  \centering
  \includegraphics[width=0.5\textwidth]{./images02/autocorrelation/same-bit-histogram.png}

@@

\begin{figure}[h!]
  \centering
  \subfloat[$\text{addr}_i=1$]{\includegraphics[width=0.5\textwidth]{./images02/autocorrelation/x_at_x_addr1.png}}

  \subfloat[$\text{addr}_i=0$]{\includegraphics[width=0.5\textwidth]{./images02/autocorrelation/x_at_x_addr0.png}}

@@

\begin{figure}[h!]
  \centering
  \subfloat[``random at x'']{\includegraphics[width=0.5\textwidth]{./images02/autocorrelation/random_at_x_counters.png}}

  \subfloat[``x at x'']{\includegraphics[width=0.5\textwidth]{./images02/autocorrelation/x_at_x_counters.png}}

@@

\begin{figure}[h!]
  \centering
  \subfloat[Equation \ref{eqn:sdm-eta1-addr1}  ($\text{addr}_k=1)$]{\includegraphics[width=0.5\textwidth]{./images02/autocorrelation/read-counters-eta1_addr1.png}}

  \subfloat[Equation \ref{eqn:sdm-eta1-addr0} ($\text{addr}_k=0$)]{\includegraphics[width=0.5\textwidth]{./images02/autocorrelation/read-counters-eta1_addr0.png}}

@@

\begin{figure}[h!]
  \centering
  \subfloat[Equation \ref{eqn:sdm-eta1}  ($\eta_k=1)$]{\includegraphics[width=0.5\textwidth]{./images02/autocorrelation/read-counters-eta1.png}}

  \subfloat[Equation \ref{eqn:sdm-eta0} ($\eta_k=0$)]{\includegraphics[width=0.5\textwidth]{./images02/autocorrelation/read-counters-eta0.png}}

@@

\begin{figure}[!htb]
  \centering
  \includegraphics[width=0.5\textwidth]{./images02/autocorrelation/read-random-bs.png}

@@

\begin{figure}[!htb]
  \centering
  \includegraphics[width=0.5\textwidth]{./images02/autocorrelation/single-read-dist.png}

### 2018-08-22 paperIEEE.tex
some fucking graphics finally appear

%% LyX 2.3.0 created this file.  For more info, see http://www.lyx.org/.
%% Do not edit unless you really know what you are doing.

\RequirePackage{fix-cm} % fix some latex issues see: http://tug.org/texmf-dist/doc/latex/base/fixltx2e.pdf

\documentclass[twocolumn,journal]{IEEEtran}
\usepackage[T1]{fontenc}
\usepackage[latin9]{inputenc}
\usepackage{calc}
\usepackage[unicode=true,
 bookmarks=true,bookmarksnumbered=true,bookmarksopen=true,bookmarksopenlevel=1,
 breaklinks=false,pdfborder={0 0 0},pdfborderstyle={},backref=false,colorlinks=false]
 {hyperref}
\hypersetup{pdftitle={Your Title},
 pdfauthor={Your Name},
 pdfpagelayout=OneColumn, pdfnewwindow=true, pdfstartview=XYZ, plainpages=false}

@@

\makeatother

@@

\begin{IEEEkeywords}
Sparse Distributed Memory, Autocorrelation, Neural Networks, Memory,
Systemwide properties.
\end{IEEEkeywords}

@@

In this other paragraph we explain what the equator distance is. Then,
this introductory section breaks and moves on to the main findings
of this paper.

\begin{figure}[!htb]
\centering\includegraphics{./images02/calculated-table-72.png}
\caption{Kanerva's original Figure 7.3 generated using the equations from \citet{brogliato2014sparse}.
\label{fig:kanerva-figure-73-calculated}
}
\end{figure}

\input{./Chapters/sdm-autocorrelation.tex}

>>>>

% Preview source code

%% LyX 2.3.0 created this file.  For more info, see http://www.lyx.org/.
%% Do not edit unless you really know what you are doing.
\documentclass[twocolumn,journal]{IEEEtran}
\usepackage[T1]{fontenc}
\usepackage[latin9]{inputenc}
\usepackage{calc}
\usepackage{graphicx}
\usepackage[unicode=true,
 bookmarks=true,bookmarksnumbered=true,bookmarksopen=true,bookmarksopenlevel=1,
 breaklinks=false,pdfborder={0 0 0},pdfborderstyle={},backref=false,colorlinks=false]
 {hyperref}
\hypersetup{pdftitle={Your Title},
 pdfauthor={Your Name},
 pdfpagelayout=OneColumn, pdfnewwindow=true, pdfstartview=XYZ, plainpages=false}

@@

% !TEX root = ../partial-sdm.tex

\@ifundefined{showcaptionsetup}{}{%
 \PassOptionsToPackage{caption=false}{subfig}}
\usepackage{subfig}
\makeatother

@@

\begin{IEEEkeywords}
Sparse Distributed Memory, Autocorrelation, Theoretical Neuroscience, Memory,
Systemwide properties.
\end{IEEEkeywords}

@@

\begin{figure}[h!]
  \centering
  \subfloat[$\text{addr}_i=1$]{\includegraphics[width=0.5\textwidth]{./images02/autocorrelation/x_at_x_addr1.png}}

  \subfloat[$\text{addr}_i=0$]{\includegraphics[width=0.5\textwidth]{./images02/autocorrelation/x_at_x_addr0.png}}

  \caption{The value of the counters after $s=10,000$ writes shows the autocorrelation in the counters in autoassociative memories (``x at x''). The histogram was obtained through simulation. The red curve is the theoretical normal distribution found in equations (\ref{cntaddr1}) and (\ref{cntaddr0}).}
  \label{fig:DELETE-sdm-corr-counters}
\end{figure}

\begin{figure}[h!]
\centering

\includegraphics[width=\columnwidth]{./images02/autocorrelation/autocorrelation_n=1000_closeview=False.eps}

\caption{The threshold size $r$ of hard-locations bring about the autocorrelation of Theorem \ref{T1}. Consider, for instance, the extremes \{0, $n$\}.  Let us start with $n$ (in our case, $n=1000$ dimensions): given the information that $d(x,y)\le n$, the probability of a bitmatch in dimension $i$ is $1/2$; as $\forall x,y \in \{0, 1\}^N, d(x,y)\le n$. At the other extreme, consider that we have the information that $d(x,y)\le 0$: in this case $x=y$ and the probability of a bitmatch, in any dimension, is 1. The autocorrelation hence drops monotonically until convergence at $1/2$ as the distance grows. Numerically, our results converge to precisely $1/2$ only after $d(x,y)\ge 607$ for $n=1000$; $d(x,y)\ge 5332$ for $n=10000$, and $d(x,y)\ge 83$ for $n=100$. This will be seen in Lemma \ref{thm:sdm-access-radius}.
\label{fig:bitmatchbias}}
\end{figure}

In this other paragraph we explain what the equator distance is.

Then, this introductory section breaks and moves on to the main findings
of this paper.

\input{Chapters/sdm-autocorrelation.tex}
